---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# envlogger

<!-- badges: start -->
<!-- badges: end -->

Functions to handle EnvLogger data, from reading, processing and plotting.  
If data conforms to the CCTBON naming scheme, additional functionalities are available.

## Installation

You can install the development version of **envlogger** from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ruiseabra/envlogger")
```

## Load envlogger
```{r load}
library(envlogger)
```

## read
```{r read}
# here we use the package's example data
READ_ENV(env_example("nozzz"), just_rep = TRUE)
```

## cctbon

If the dataset being read conforms to CCTBON guidelines, especially regarding to the logger naming scheme, additional information can be extraceted.
```{r cctbon}
# here we use the package's example data
cctbon_id(READ_ENV(env_example("nozzz"), just_rep = TRUE))
```

## plot

Envlogger data can be visualized very quickly with simple commands.

```{r plot1}
plot_env(
  cctbon_data = env_example("ptzzw", no_logs = TRUE)[1], 
  by_day = FALSE
  )
```

When plotting complex datasets, `plot_env()` offers a great deal of customization through the use of several function parameters.
```{r plot2}
plot_env(
  cctbon_data = env_example(c("nozzz", "ptzzy", "ptzzw")),
  by_micro  = TRUE,
  col_by    = "sh",
  facet_row = "exp",
  ribbon    = TRUE,
  stat      = "q75",
  roll_days = 7
  )
```
